First steps towards a formalization of Forcing \\ Revisions made to the paper

### 2018-11-18 LSFA/cover_letter.tex
recursion en Names
responder al Reviewer 3 sobre el esfuerzo y el carácter del trabajo y por qué no agregamos nada de lo que dice la conclusión.

The section on ``Names'' includes two new applications. One is the
proof that the generic
extension $M[G]$ is a transitive set. The second one is even more basic  and
was missing in the two previous versions of the manuscript: The
generic filter $G$ belongs to $M[G]$. 
%
%
\bibliographystyle{arXiv/mi-estilo-else}
\bibliography{citados}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% ispell-local-dictionary: "american"
%%% End:

>>>>

The section on ``Names'' includes a thorough discussion on recursive
definitions in Isabelle/ZF and two new applications. One is the
proof that the generic
extension $M[G]$ is a transitive set. The second one is even more basic  and
was missing in the two previous versions of the manuscript: The
generic filter $G$ belongs to $M[G]$.

We take this opportunity to answer a question by Reviewer 3 from the
first round of corrections. Obtaining the results of this paper per se
was not very difficult. But as this Reviewer points out, the setting
up for the project, planning a strategy, and even studying Paulson's
libraries%
%%%%%%%%%%%%%%%%%%%%
\footnote{Even today we find ourselves inadvertently reproving some
  variant of a lemma in Paulson's development on set theory.}
%%%%%%%%%%%%%%%%%%%%
took almost an year of work. With the hindsight of this planning period,
we would like to point out that most of the results stated in the
conclusion section involve some serious development; even  a
publication for each item. It is therefore not feasible to include
none of them in this revision.
%
%
\bibliographystyle{arXiv/mi-estilo-else}
\bibliography{citados}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% ispell-local-dictionary: "american"
%%% End:
